An agent-based model for city networks based on interactions between firms

### 2020-03-04 main.tex

The use of network models to understand processes underlying the emergence and dynamics of such urban networks has already been widely tackled in the literature. \cite{dai2016simulating} propose a generative urban network model at the regional scale, combining geographical factors with network topological properties. Air transportation networks can also be understood as urban networks, and \cite{zanin2013modelling} reviews several models for such networks. Trade network have been extensively studied from the viewpoint of complex networks, but are generally driven at the country-level \cite{garlaschelli2005structure}. Input-output models, mostly used in Regional science to represent flows between geographical areas, are considered some cases a type of urban generative model \cite{jin1993generation}. In that stream of research, spatial interaction models \cite{dennett2013multilevel} can form the basis of urban network models for abstract flows \cite{dai2016generative} or physical infrastructure \cite{raimbault2020indirect}.

@@

% je suis nulle avec overleaf, mais est-ce possible de mettre la biblio dans un ordre alphabétique? J'imagine qu'il y a un moyen pour le faire d'une maniere non manuelle.
% -> switch de unsrt a apalike

% \bibliographystyle{apalike}
\bibliographystyle{unsrt}
\bibliography{biblio}

>>>>

The use of network models to understand processes underlying the emergence and dynamics of such urban networks has already been widely tackled in the literature. \cite{dai2016simulating} propose a generative urban network model at the regional scale, combining geographical factors with network topological properties. Air transportation networks can also be understood as urban networks, and \cite{zanin2013modelling} reviews several models for such networks. Trade network have been extensively studied from the viewpoint of complex networks, but are generally driven at the country-level \cite{garlaschelli2005structure} because of scarce data at city-level. Input-output models, mostly used in Regional science to represent flows between geographical areas, are considered in some cases as a type of urban generative model \cite{jin1993generation}. In this stream of research, spatial interaction models \cite{dennett2013multilevel} can form the basis of urban network models for abstract flows \cite{dai2016generative} or physical infrastructure \cite{raimbault2020indirect}.

@@

\bibliographystyle{apalike}
%\bibliographystyle{unsrt}
\bibliography{biblio}
